### 2017-11-29 manuscript.rmd
reworked intro, did not regenerate pdf

Siphonophores are a group of 188 valid species within Hydrozoa (Cnidaria), the vast majority of which are members of the plankton (fig. 1). Siphonophores are colonial, and are composed of zooids that are each homologous to solitary animals, but are physiologically integrated [@totton1965synopsis; @mackie1988siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial hydrozoans in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. A siphonophore colony arises from a single embryo, which forms a protozooid and a growth zone from which other genetically identical zooids bud asexually [@carre1969etude;@carre1991complete;@carre1967;@carre1995ordre]. Each zooid is generated asexually, arises in the same repeating species-specific pattern, and is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution]. Siphonophores are found at all depths - most species are planktonic, with the exception of one pleustonic species (*Physalia physalis*, Portuguese man of war) that lives at the interface of water and air, and a small clade of benthic siphonophores, the Rhodaliidae [@carre1995ordre;@Totton1960;@pugh1983benthic]. They are among the most abundant gelatinous predators in the open ocean, and play an important ecological role in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous].

Siphonophores are monophyletic and nested within the Hydroidolina, although relationships among the major lineages of the Hydroidolina remain difficult to resolve [@cartwright2010character;@Cartwright2008kl;@zapata2015phylogenomic]. The most resolved siphonophore phylogeny to date focused on two genes (16S, 18S) from 52 siphonophore taxa, and resolved many long standing questions about siphonophore biology, including the relationships of the three historically recognised groups (Cystonectae, Physonectae, and Calycophorae) [@Dunn:2005dy]. The cystonects were found to be sister to all other siphonophores, while the calycophorans were nested within physonects (the name Codonophora was given to this clade)[@Dunn:2005dy].

@@

The Apolemiidae are sister to all other Codonophora, however there was little resolution of deep relationships within Codonophora. The history of colony structure and budding was investigated by mapping these traits to the tree, and suggesting a complex history of zooid gain and loss. Resolving deep relationships within Codonophora is key to resolving the evolution of several character traits, including sexual systems (monoecy vesus dioecy) or the gain and loss of particular zooids, such as palpons.

Siphonophores are difficult to collect, in part because they are fragile (nets destroy all but the most robust parts of the colony), but also because many species are found in the deep sea [@youngbluth1984water;@Dunn:2005dy]. Specimen sampling for the previous phylogeny, and this new work, is enabled by modern collection techniques, including blue-water scuba diving and remotely operated vehicles (ROVs). Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 34 siphonophore species and 9 outgroup species. Using 1071 genes shared across species, we are able to resolve deep relationships within the siphonophore phylogeny and reconstruct the evolutionary history of characters, including zooid type, life history traits, and habitat.

>>>>

Siphonophores (Fig. 1) are among the most abundant gelatinous predators in the open ocean, and play an important ecological role in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous]. Siphonophores, which belong to Hydrozoa (Cnidaria), are found at all depths in the ocean. *Physalia physalis*, the Portuguese man of war, floats at the surface and, as a result, is the most familiar siphonophore species. Most siphonophores species are planktonic, living in the midwater where some grow to be longer than 30 meters in length. There is also a small clade of benthic siphonophores, the Rhodaliidae [@carre1995ordre;@Totton1960;@pugh1983benthic], that are tethered to the bottom for part of their lives. In all, there are currently 188 valid described species.

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years (XXX) due to their very unique structure and development. Like many other cnidarians, they are colonial -- they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animals, but are physiologically integrated [@totton1965synopsis; @mackie1988siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating species-specific pattern.

@@

Understanding the unique ecology, morphology, and development of siphonophores requires an understanding of their phylogenetic relationships. The relationship of siphonophores to other hydrozoans has been difficult to resolve [@cartwright2010character; @Cartwright2008kl; @zapata2015phylogenomic], but there has been progress on their internal relationships. A siphonophore phylogeny [@Dunn:2005dy] based on two genes (16S, 18S) from 52 siphonophore taxa advanced serveral long standing questions about siphonophore biology. These include the relationships of the three historically recognised groups, Cystonectae, Physonectae, and Calycophorae. The cystonects were found to be sister to all other siphonophores, while the calycophorans were nested within physonects. The name Codonophora was given to this clade of physonects and calycophorans [@Dunn:2005dy].

Major questions remained after this early work, though. There was, in particular, little support for important deep relationships within Codonophora. Resolving deep relationships within Codonophora is key to resolving the evolution of several character traits, including sexual systems (monoecy vesus dioecy) or the gain and loss of particular zooids, such as palpons. Here we present a broadly sampled phylogenomic analysis of Siphonophora, assessing transcriptomic data from 34 siphonophore species and 9 outgroup species. Using 1071 genes shared across species, we find strong support for imporant relationships within the siphonophore phylogeny. Using this phylogeny, we reconstruct the evolutionary history of characters central to their unique biology, including zooid type, life history traits, and habitat.
